### 2017-08-16 README.Rmd
re-structure tmle-ate, other misc changes

`methyvim` is an R package that provides facilities for differential methylation
analysis based on _variable importance measures_ (VIMs), a class of statistical
estimable target parameters that arise in causal inference.

@@

1. Pre-screening of genomic sites is used to isolate a subset of sites for
which there is cursory evidence of differential methylation. For the sake of
computational feasibility, targeted minimum loss-based estimates of VIMs are
computed only for this subset of sites. Several screening approaches are
available, adapting core routines from the following R packages:
[`limma`](http://bioconductor.org/packages/release/bioc/html/limma.html),
[`tmle.npvi`](https://CRAN.R-project.org/package=tmle.npvi).
2. Nonparametric VIMs are estimated for the specified parameter, currently using
routines from the R packages
[`tmle.npvi`](https://CRAN.R-project.org/package=tmle.npvi) (to estimate the
NPVI parameter) or [`tmle`](https://CRAN.R-project.org/package=tmle) (to
estimate the ATE).
3. Since pre-screening is performed prior to estimating VIMs, we make use of a
multiple testing correction uniquely suited to such settings. Rather generally,
the Benjamini & Hochberg procedure for controlling the False Discovery Rate
(FDR) [@benjamini1995controlling] is applied due to multiple testing issues
inherent to the estimation procedure. Specifically, we apply a modified marginal
Benjamini & Hochberg step-up False Discovery Rate controlling procedure for
multi-stage analyses (FDR-MSA) [@tuglus2009modified].

@@

After using the `methyvim` R package, please cite both of the following:

        @article{hejazi2017methyvim,
          doi = {},
          url = {},
          year  = {2017},
          month = {},
          publisher={Faculty of 1000 Ltd},
          volume = {},
          author = {Hejazi, Nima S. and Hubbard, Alan E. and {van der Laan},
            Mark J.},
          title = {methyvim: Differential methylation analysis with targeted
            nonparametric variable importance measures},
          journal = {F1000Research}
        }

        @misc{hejazi2017methyvim-r,
          doi = {},
          url = {},
          howpublished = {\url{https://github.com/nhejazi/methyvim}},
          year  = {2017},
          author = {Hejazi, Nima S. and Hubbard, Alan E. and {van der Laan},
            Mark J.},
          title = {methyvim: Differential methylation analysis with targeted
            minimum loss-based estimates of variable importance measures}
        }

>>>>

`methyvim` is an R package that provides facilities for differential methylation
analysis based on _variable importance measures_ (VIMs), a class of
statistically estimable target parameters that arise in causal inference.

@@

1. Pre-screening of genomic sites is used to isolate a subset of sites for
which there is cursory evidence of differential methylation. For the sake of
computational feasibility, targeted minimum loss-based estimates of VIMs are
computed only for this subset of sites. Several screening approaches are
available, adapting core routines from the following R packages:
[`limma`](http://bioconductor.org/packages/release/bioc/html/limma.html),
[`tmle.npvi`](https://CRAN.R-project.org/package=tmle.npvi).
2. Nonparametric VIMs are estimated for the specified parameter, currently using
routines from the R packages
[`tmle.npvi`](https://CRAN.R-project.org/package=tmle.npvi) (to estimate the
NPVI parameter) or [`tmle`](https://CRAN.R-project.org/package=tmle) (to
estimate the ATE).
3. Since pre-screening is performed prior to estimating VIMs, we make use of a
multiple testing correction uniquely suited to such settings. Due to the
multiple testing nature of the estimation problem, a variant of the Benjamini &
Hochberg procedure for controlling the False Discovery Rate (FDR) is applied
[@benjamini1995controlling]. Specifically, we apply the modified marginal
Benjamini & Hochberg step-up False Discovery Rate controlling procedure for
multi-stage analyses (FDR-MSA) [@tuglus2009modified].

@@

After using the `methyvim` R package, please cite the following:

        @article{hejazi2017methyvim,
          doi = {},
          url = {},
          year  = {2017},
          month = {},
          publisher={Faculty of 1000 Ltd},
          volume = {},
          author = {Hejazi, Nima S and Hubbard, Alan E and {van der Laan}, Mark
            J},
          title = {methyvim: Differential methylation analysis with targeted
            esitmates of nonparametric variable importance measures},
          journal = {F1000Research}
        }
